Analysis Pipeline

### 2023-11-16 analyses.RmD
- fixed one item
- implemented feedback from reviewers

# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
              "pwr", "semPlot", "semTools", "tidyverse", "td")

@@

vars_pri <- c("NFP_SOC", "NFP_PHY", "NFP_PSY",
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")
vars_pri_txt <- c("Social", "Physical", "Psychological",
                  "Companies", "Governnment",
                  "Anonynmity", "Infornmational", "General")
vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
                  "Companies", "Govern-\nment",
                  "Anony-\nmity", "Infor-\nmational", "General")
vars_pri_txt_abr <- c("Social", "Phys.", "Psych.",
                  "Comp.", "Gov.",
                  "Anonym.", "Inform.", "General")

@@

 1.	I don’t like it when strangers come too close to me.
 2.	I don’t like to stand in a dense crowd of people.
 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
 4.	I hate it when people enter my personal space uninvited.

@@

# Power Analyses

@@

@@

reg_fig <- ggplot(tab_reg, aes(x = Estimate, y = Predictor)) + 
  coord_cartesian(xlim = c(-.5, .5)) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_vline(xintercept = -.1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
  geom_vline(xintercept = .1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(size = 1.5, position = position_dodge(-.7)) +
  scale_x_continuous(breaks = c(-.3, 0, .3)) + 
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    # panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 1),
    legend.position = "none"
    ) + 
    facet_grid(Predictor_cat ~ `Need for privacy`, scales = "free_y")
suppressWarnings(print(reg_fig, warning = F))

>>>>

# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
              "pwr", "semPlot", "simsem", "semTools", "tidyverse", "td")

@@

vars_pri <- c("NFP_SOC", "NFP_PHY", "NFP_PSY",
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")
vars_pri_txt <- c("Social", "Physical", "Psychological",
                  "Companies", "Governnment",
                  "Anonynmity", "Informational", "General")
vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
                  "Companies", "Govern-\nment",
                  "Anony-\nmity", "Infor-\nmational", "General")
vars_pri_txt_abr <- c("Social", "Phys.", "Psych.",
                  "Comp.", "Gov.",
                  "Anonym.", "Inform.", "General")

@@

 1.	I don’t like it when strangers come too close to me.
 2.	I don’t like to stand in a dense crowd of people.
 3.	I don’t like to sit next to a stranger on a train, bus, or plane.
 4.	I hate it when people enter my personal space uninvited.

@@

# Power Analyses
## Rudimentary

@@

## Detailed: Simple

```{r}
population <- 
  "
  # Fix means to 0
  HEX_HOH_SIN_01 ~ 0*1
  HEX_HOH_SIN_02 ~ 0*1
  HEX_HOH_SIN_03 ~ 0*1
  HEX_HOH_SIN_04 ~ 0*1
  NFP_PHY_01 ~ 0*1
  NFP_PHY_02 ~ 0*1
  NFP_PHY_03 ~ 0*1
  NFP_PHY_04 ~ 0*1

  # Fix variances
  HEX_HOH_SIN_01 ~~ 1 * HEX_HOH_SIN_01
  HEX_HOH_SIN_02 ~~ 1 * HEX_HOH_SIN_02
  HEX_HOH_SIN_03 ~~ 1 * HEX_HOH_SIN_03
  HEX_HOH_SIN_04 ~~ 1 * HEX_HOH_SIN_04
  NFP_PHY_01 ~~ 1 * NFP_PHY_01
  NFP_PHY_02 ~~ 1 * NFP_PHY_02
  NFP_PHY_03 ~~ 1 * NFP_PHY_03
  NFP_PHY_04 ~~ 1 * NFP_PHY_04

  # Define latent vars
  HEX_HOH_SIN =~ .9*HEX_HOH_SIN_01 + .9*HEX_HOH_SIN_02 + .9*HEX_HOH_SIN_03 + .9*HEX_HOH_SIN_04
  NFP_PHY =~ .9*NFP_PHY_01 + .9*NFP_PHY_02 + .9*NFP_PHY_03 + .9*NFP_PHY_04

  # Covariances
  HEX_HOH_SIN ~~ .1*NFP_PHY
  "
sample <- "
  HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
  NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
"

reliability <- sim(
  # nRep = NULL, 
  model = sample, 
#  n = 500,
  n = seq(500, 5000, 50), 
  generate = population, 
  # std.lv = TRUE, 
  lavaanfun = "sem"
  )

summary(reliability)
power_tab <- getPower(reliability)
power_80 <- findPower(power_tab, "N", 0.90)
power_80["HEX_HOH_SIN~~NFP_PHY"]
```

@@

# make figure
reg_fig <- ggplot(tab_reg, aes(x = Estimate, y = Predictor)) + 
  coord_cartesian(xlim = c(-.5, .5)) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_vline(xintercept = -.1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
  geom_vline(xintercept = .1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(size = 1.5, position = position_dodge(-.7)) +
  scale_x_continuous(breaks = c(-.3, 0, .3)) + 
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    # panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 1),
    legend.position = "none"
    ) + 
    facet_grid(Predictor_cat ~ `Need for privacy`, scales = "free_y")
suppressWarnings(print(reg_fig, warning = F))

### 2023-11-16 analysis_pipeline.Rmd
- implemented feedback from reviewers

# Model Fit

 - If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
 - If these changes do not yield sufficient fit, we will drop malfunctioning items. 
 - If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
 - EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 
 - If more than one dimension is revealed, we will implement bifactor model solutions.[^1] 
 - Bifactor models retain a general measure of the variable, without introducing novel potentially overfitted subdimensions.
 - If no adequate bifactor model can be found, we will proceed by deleting items with low loadings on the general factor and/or the specific factors. 
 - If also after deletion of individual items no bifactor solution should emerge, we will use a subset of the items to extract a single factor with sufficient factorial validity.

>>>>

# Factorial validity

We will inspect the factorial validity of the privacy and personality variables as follows.

 - We run a model with all personality and privacy variables as we originally configured them in a confirmatory factor analysis.
 - If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariances or cross-loadings if theoretically plausible. 
 - If these changes do not yield sufficient fit, we will drop malfunctioning items, while having at least three items per dimension/facet.
 - If this should not work out, we will run Exploratory Structural Equation Modelling using oblimin rotation, allowing all personality items to load on the same factors, while allowing all privacy items to load on the same factors.
 - If fit is still subpar, we will conduct in-depth exploratory factor analyses (EFA) to asssess the underlying factor structure. 
 - EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 
 - If more than one dimension is revealed, we will implement bifactor model solutions.[^1] 
 - Bifactor models retain a general measure of the variable, without introducing novel potentially overfitted subdimensions.
 - If no adequate bifactor model can be found, we will proceed by deleting items with low loadings on the general factor and/or the specific factors. 
 - If also after deletion of individual items no bifactor solution should emerge, we will use a subset of the items to extract a single factor with sufficient factorial validity.
